Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-08 paper/ijcai/paper.tex
small fix

The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
project. Table \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.

>>>>

The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
project. Table , reports the average rank of all faulty statements for each version of \chart{} project after
applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.
